SDM\_the\_search\_for\_powers\_of\_2\_everywhere

### 2018-04-27 Chapters/hathor-architecture.tex
The incredible animal behavior of Dr Linhares
Hathor: reorganizing the text.

This work introduces the Hathor's architecture which lies between Bitcoin's and Iota's and may be a solution to scaling, centralization, and spam issues. Like Iota, new transactions confirm others, forming a Directed Acyclic Graph (DAG). For this, each transaction has its own proof-of-work which is solved by the issuer before propagating the transactions in the network. Like Bitcoin, miners find new ``blocks'' every 10 minutes in which they collect the fees and newly generated tokens. Each transaction has an ``accumulated weight'' which express the required effort to break the transaction, similar to Bitcoin's number of confirmations.

This way, there will be two difficulty levels in the system: one for new transactions which are just moving tokens around, and another one for ``blocks'' which are generating new tokens and collecting fees. The first may be adjusted to prevent spammers, which would spend too many resources to generate a great number of new transactions. The second is adjusted every 2,016 blocks to keep the pace of block on every 2 minutes.

There is a trade-off about the required proof-of-work of new transactions. The higher it is, the harder it is to generate new transactions, preventing spammers but also making it harder for IoT devices generate new transactions.

Each transaction has to confirm all its inputs, i.e., there must be a confirmation path between all the transactions of the inputs and the transaction which are spending them. It is always possible since there is at least one confirmation path between any transaction and a tip. This is important for security reasons.

The transactions are classified into three groups: (i) confirmed transactions, (ii) in-progress transactions, and (iii) unconfirmed transactions (tips). The confirmed transaction are the ones which have already been settled, i.e., their accumulated weights have reached a minimum level. The unconfirmed transactions (tips) are the brand new transactions which have not been confirmed even once yet, i.e., their accumulated weights are zero. The in-progress transactions are in the middle. They have already been confirmed a few times, but not enough to reach the minimum level required to be a confirmed transaction.

A ``block'' is just a regular transaction with no inputs which confirms a previous block and at least two in-progress transactions or tips. There may be any number of outputs provided that they comply with the number of newly generated tokens. Each block collects all fees from all transactions confirmed by it which have not been confirmed by another block before.

In the low load scenario, there is a small number of new transactions coming into the network, which means they give a minor contribution to confirmations. In this case, the confirmation is held mostly by ``blocks''. On the other hand, in the high load scenarios, there is a large number of new transactions giving a major contribution to confirmations. In this case, the ``blocks'' strengthen the confirmation, but most of them will have already been confirmed before the new blocks are found. The higher the number of new transaction, the faster the transactions are confirmed. The blocks assure a ``maximum confirmation time''.

The incentive scheme which keeps the network running is the same as Bitcoin's. Miners go towards fees and newly generate coins, while users go towards exchanging their tokens.

@@

The concepts of weight and accumulated weight are the same as Iota's, but their equations are different. The weight of a transaction is calculated as $\log_2(k)$ where $k$ is the average number of hashes required to solve its proof-of-work again, while the accumulated weighted of a transaction A with weight $w_A$ is calculated as $\log_2(2^{w_A} + \sum_{A \leadsto P} 2^{w_P})$. The $\log$ function is used to reduce the magnitude of the numbers. Hence, the power-of-2 of the accumulated weight is a measure of the average number of hashes required to solve the proof-of-work of all transactions that are confirming A.

@@

The hash function used for the proof-of-work (PoW) is the same as Bitcoin: \emph{SHA-256} applied twice. Thus, most of the math analysis we have done before is just the same.

@@

Notice that, if the hash rate does not change, then $\Delta t = 128 \cdot 2016$ and $w_\text{new} = w_\text{old}$.

@@

$$w_\text{tx} = \left\lfloor \log_2(\text{size}) + \log_2(\text{amount}) + 0.5 \right\rfloor$$

Although the transaction size may change a bit depending on the implementation, a typical transaction with 2 inputs and 2 outputs would have 188 bytes. So, for instance, transfering 50,000 tokens would require a weight of 23, which means an average of $2^{23}$ trials to solve the PoW.

@@

@@

Using the same strategy, Hathor's issuance rate starts in 50,000 tokens per block and decreases over time. Different from Bitcoin, Hathor's tokens are always integers and cannot be split. Every 1,000,000 blocks, the number of tokens issued per block is halved. Thus, the supply is limited to 100 billion issued tokens during its whole life. To calculate the supply limit use the following equation:

\begin{align*}
    \sum_{k=0}^{\infty} 1,000,000 \cdot \left\lfloor \frac{50000}{2^k} \right\rfloor \approx
    \sum_{k=0}^{\infty} 1,000,000 \cdot \frac{50000}{2^k} = 100 \text{ billion}
\end{align*}

As the average time between blocks is 128 seconds, it will take around 3 years, 9 months and 20 days between halves.

@@

The value of the fee is calculate as the difference between the transaction's outputs and the inputs. For instance, a transaction with inputs summing 10,000 HTR and outputs summing 9,000 HTR are paying 1,000 HTR of fees.

Each transaction may pay a fee to the next block which confirms it. But, even if the fee is zero, the miners are forced to confirm at least two pending transactions (in-progress or unconfirmed), and these pending transactions confirms other transactions which may have no fees. In summary, transactions with no fees cannot be left behind and will always be confirmed by both blocks and other transactions.

One may arguee that it allows the whole network to never pay fees and they are right. In the beginning, miners' incentive is driven by new tokens instead of fees. In the long term, it may be necessary to require a minimum fee to keep the miners working.

@@

A transaction will be considered valid when it complies with the following rules: (i) it spends only unspent outputs; (ii) the sum of the inputs is greater than or equal to the sum of the outputs; (iii) the number of inputs is at most 256; (iv) the number of outputs is at most 256; (v) it confirms at least two pending transactions; (vi) it solves the PoW with the correct weight.

The transaction has a time field which is used to inform when the transaction was generated. The time field must be in UTC time and may be within at most 60 minutes from the current time. Otherwise, the transaction will be discarded.

In case of transaction conflict, in which two transactions try to spend the same tokens, the one with higher accumulated weight is chosen and the other is invalidated. Although it is not possible in Iota because of the submarine attack, Hathor does not have the same problem. In Hathor, like in Bitcoin, the submarine attack is only possible if the attacker has a hash rate higher than the whole network, including the miners. In other words, when analysing the double spending attack, Hathor is as safe as Bitcoin.

@@

Services of solving proof-of-work may also be offered by companies. They give their customers a wallet address and they send the payment inside of the transaction itself. This allows IoT devices to save energy or to delegate the task of solving the PoW to whoever is receiving the tokens.

@@

There is no orphan blocks in Hathor. Unless a block confirms either directly or indirectly an invalid transaction, every block is valid. There is no need to left a block behind since its proof-of-work is also protecting transactions.

\section{Network}

Like in all other cryptocurrencies, nodes will communicate through a peer-to-peer network. They will exchange transactions and blocks, verifying whether they are valid or not, while they will also answer queries.

Thus, if a thin client wants to transfer some tokens, it just connects to the network and queries for the tips. With the response, it solves the proof-of-work and propagates the new transaction. In order to avoid malicious nodes, the thin client may ask to more than one node and randomly pick two transactions.

>>>>

% !TEX root = ../partial-blockchain.tex

This work introduces the Hathor's architecture which lies between Bitcoin's and Iota's and may be a solution to scaling, centralization, and spam issues.

Like Iota, new transactions confirm others, forming a Directed Acyclic Graph (DAG). For this, each transaction has its own proof-of-work which is solved by the issuer before propagating the transactions in the network. Like Bitcoin, miners find new ``blocks'' every 10 minutes in which they collect the fees and newly generated tokens. Each transaction has an ``accumulated weight'' which express the required effort to break the transaction, similar to Bitcoin's number of confirmations.

In Hathor, there are two difficulty levels: (i) one for new transactions which are just moving tokens around, and (ii) another one for ``blocks'' which are generating new tokens and collecting fees. The first may be adjusted to prevent spammers, which would spend too many resources to generate a great number of new transactions, whereas the latter is adjusted every 2,016 blocks to keep the pace of blocks on every 2 minutes.

Both miners and users will be working on proof-of-work, decentralizing even more the network's hash rate. Even though the users' difficulty is less than the miners', the hash rate will increase every new user. The more transactions arrive, the higher the total hash rate. It may have good consequences in governance, which we will further discuss.

There is a trade-off about the difficulty of new transactions. The higher it is, the harder it is to generate new transactions, preventing spammers but also making it harder for IoT devices generate new transactions. This difficulty may even be increased when a spam attack is in course and reduced when it is gone. If the difficulty is too high, IoT devices may sign their transactions and send them to another devices which have a greater hash rate and will solve their proof-of-work faster.

It also seems interesting to have this difficulty depending on new transaction's size (in bytes) and amount being moved. The idea here is to require more work when high amounts are at stake. It would not affect IoT devices, which are expected to usually move smaller amounts. Regarding the transaction's size, requiring more work for bigger transactions may make sense because they may prevent abuses, such as a denial-of-service attack using enormous transactions which would consume a lot of node's bandwidth and disk space.

Another important security matter is that each transaction has to confirm all its inputs, i.e., there must be a confirmation path between all the transactions of the inputs and the transaction which are spending them. It is always possible since there is at least one confirmation path between any transaction and a tip. It ensures that, when a conflict is resolved, only the sub-DAG with root at the invalidated transaction will be affected. The remaining of the DAG remains the same.

The transactions are classified into three groups: (i) confirmed transactions, (ii) in-progress transactions, and (iii) unconfirmed transactions (tips). The confirmed transaction are the ones which have already been settled, i.e., their accumulated weights have reached a minimum level. The unconfirmed transactions (tips) are the brand new transactions which have not been confirmed even once yet, i.e., their accumulated weights are zero. The in-progress transactions are in the middle. They have already been confirmed a few times, but not enough to reach the minimum level required to be a confirmed transaction. For simplicity, the pending transactions encompass both in-progress and unconfirmed transactions.

A \emph{block} is just a regular transaction with no inputs which confirms a previous block and at least two in-progress transactions or tips. There may be any number of outputs provided that they comply with the number of newly generated tokens. Each block collects all fees from all transactions confirmed by it which have not been confirmed by another block before. The blocks are ordered according to their timestamp. If two blocks have the same timestamp, the block hash is used as a tiebreaker.

In the low load scenario, there is a small number of new transactions coming into the network, which means they give a minor contribution to confirmations. In this case, the confirmation is held mostly by blocks. On the other hand, in the high load scenarios, there is a large number of new transactions giving a major contribution to confirmations. In this case, the blocks strengthen the confirmations, but many of them will have already been confirmed before the next blocks are found. The higher the number of new transaction, the faster the transactions are confirmed. The blocks assure a ``maximum confirmation time''.

The incentive scheme which keeps the network running is the same as Bitcoin's. Miners go towards fees and newly generate coins, whereas users just want to exchange their tokens. When there is no new transcation to be confirmed, the miners keep the network up and running while they find new blocks.

@@

Hathor uses similar concepts of weight and accumulated weight as Iota's. The weight depends only in the transaction itself, whereas the accumulated weight depends on its confirmations.

The weight of a transaction is calculated as $w = \log_2(k)$ where $k$ is the average number of hashes required to solve its proof-of-work.

The accumulated weight is the average number of hashes required to solve the proof-of-work of the transaction itself plus all the transactions which confirm it. Let $A$ be a transaction, its accumulated weight $w_A$ is calculated as $\log_2(2^{w_A} + \sum_{A \leadsto P} 2^{w_P})$.

@@

The hash function used for the proof-of-work (PoW) is the same as Bitcoin: \emph{SHA-256} applied twice. Thus, most of the math analysis we have already done before is just the same.

@@

Notice that, if the hash rate has not changed, then $\Delta t = 128 \cdot 2016$ and $w_\text{new} = w_\text{old}$.

@@

$$w_\text{tx} = \log_2(\text{size}) + \log_2(\text{amount}) + 0.5$$

Although the transaction size depends on the implementation, a typical transaction with 2 inputs and 2 outputs would have approximately 188 bytes. So, for instance, transfering 50,000 tokens would require a weight of 23, which means an average of $2^{23}$ trials to solve the proof-of-work.

@@

Hathor issues tokens every block, thus it is similar to Bitcoin. Even so, an important decision is whether it will issue a limited number of tokens or not. Bitcoin chose to issue a limited number of tokens. On the other hand, Ethereum and others chose to issue an ilimited number of tokens.

Both ways, the number of issued tokens is predictable. This feature itself brings confidence to the community, who will not face monetary intervention (unless they agree to) --- this comes in contrast with fiat money in which the central authority may change the monetary policy to adjust to political demands.

@@

%Using the same strategy, Hathor's issuance rate starts in 50,000 tokens per block and decreases over time. Different from Bitcoin, Hathor's tokens are always integers and cannot be split. Every 1,000,000 blocks, the number of tokens issued per block is halved. Thus, the supply is limited to 100 billion issued tokens during its whole life. To calculate the supply limit use the following equation:

%\begin{align*}
%    \sum_{k=0}^{\infty} 1,000,000 \cdot \left\lfloor \frac{50000}{2^k} \right\rfloor \approx
%    \sum_{k=0}^{\infty} 1,000,000 \cdot \frac{50000}{2^k} = 100 \text{ billion}
%\end{align*}

%As the average time between blocks is 128 seconds, it will take around 3 years, 9 months and 20 days between halves.

@@

In Bitcoin, the value of the fee is calculate as the difference between the transaction's outputs and the inputs. For instance, a transaction with inputs summing 8,000 and outputs summing 7,000 is paying 1,000 of fees.

In Hathor, each transaction may pay a fee to the next block which confirms it. But, even if the fee is zero, the miners are forced to confirm at least two pending transactions. These two pending transactions also confirm other transactions which may have no fees. In summary, transactions with no fees cannot be left behind and will always be confirmed by both blocks and other transactions.

One may arguee that it allows the whole network to never pay fees and they are right. In the beginning, miners' incentive is driven by new tokens instead of fees. In the long term, it may be necessary to require a minimum fee to keep the miners working, depending on the chosen issuance policy.

@@

A transaction will be considered valid when it complies with the following rules: (i) it spends only unspent outputs; (ii) the sum of the inputs is greater than or equal to the sum of the outputs; (iii) the number of inputs is at most 256; (iv) the number of outputs is at most 256; (v) it confirms at least two pending transactions; (vi) it solves the proof-of-work with the correct weight.

The transaction has a timestamp field which is used to record when the transaction was generated. This timestamp field must be in UTC time to prevent timezone issues. It must also be within at most 5 minutes from the current time, otherwise the transaction will be discarded.

@@

Services of solving proof-of-work may also be offered by companies. They give their customers a wallet address and they send the payment inside of the transaction itself. This allows IoT devices to save energy, delegating the task of solving the proof-of-work.

In case of transaction conflict, in which two transactions try to spend the same tokens, the one with higher accumulated weight is chosen and the other is invalidated. Although it is not a possible policy in Iota because of the submarine attack, Hathor does not have the same problem. In Hathor, like in Bitcoin, the submarine attack is only possible if the attacker has a hash rate higher than the whole network, including the miners. In other words, when analysing the double spending attack, Hathor is as safe as Bitcoin.

@@

Different from Bitcoin, there is no orphan blocks in Hathor. Unless a block confirms either directly or indirectly an invalid transaction, every block is valid. There is no need to left a block behind since its proof-of-work is increasing transactions' accumulated weight.

If two blocks are trying to collect fees from the same transactions, the one with higher timestamp will be discarded.

\section{Governance}

- Punishment for miners/transactions which does not comply with the rules.

- Rule change policy.

\section{Expected number of tips}

Explain transient and stationary state. The balance happens in the stationary state.

In order to estimate the balance in the number of tips, let's consider the system in which the rate of inward tips is $\lambda_\text{TX}$, while the rate of outward tips is $\rho$. Let $K$ be the number of tips in the system. Thus, after $\Delta t$ seconds, $\Delta \text{tips} = \lambda_\text{TX} \Delta t - \rho K \Delta t$. In the balance, $\Delta \text{tips} = 0$, hence $K = \frac{\lambda_\text{TX}}{\rho}$.

Finally, the rate of outward tips is twice the rate in which devices solve the proof-of-work of transactions. Let $H$ be the devices' hash rate, then, $\rho = 2 \cdot H \cdot 2^{-w_\text{TX}}$.

Twice?! It is a number between 1 and 2, but none of them.

Therefore, in the balance,

$$K = \frac{\lambda_\text{TX} \cdot 2^{w_\text{TX}}}{2H}$$

$$\frac{\lambda_\text{TX} \cdot 2^{w_\text{TX}}}{2H} \le K \le \frac{\lambda_\text{TX} \cdot 2^{w_\text{TX}}}{H}$$

\section{Attacks \& Conflicting transactions}

\section{Scripts \& Contracts}
